Ch3 process

### 2022-02-17 Ch3_samplesize/Ch3_process.Rmd
Trying to troubleshoot.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=4, fig.height=3)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

@@

```{r eval = FALSE}
# Getting weird stuff so taking this step by step
y <- 4

@@

mles.sampsizes %>% 
  mutate(mean = lomax.mean(alphas, khats))

```
```{r}
# Now calculate the cdfs for each distribution and for each threshold

@@

```{r echo=TRUE}
###################################
# Run the experiments with different sample sizes and tail thresholds

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=4, fig.height=3)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

@@

```{r echo=FALSE, eval = FALSE}
# Getting weird stuff so taking this step by step
y <- 4

@@

mles.sampsizes %>% 
  mutate(mean = lomax.mean(alphas, khats),
         tail100 = lomax.cdf(100, alphas, khats),
         tail250 = lomax.cdf(250, alphas, khats),
         tail500 = lomax.cdf(500, alphas, khats),
         tail750 = lomax.cdf(750, alphas, khats),
         tail1k = lomax.cdf(1000, alphas, khats)) %>% 
  #mutate(across(c(2:8), signif, digits=3)) %>% 
  mutate(across(starts_with("tail"), signif, digits=3))

```
```{r}
# But if we do 1-cdf, which should be P(X>=x) we get high numbers.

@@

```{r eval=FALSE, echo=FALSE}
###################################
# Run the experiments with different sample sizes and tail thresholds
